Creating importance plot

### 2020-05-13 Scripts_for_results/05_creating_importance_plot.Rmd
swapped Heatmap for heatmap.2

@@

>>>>

Heatmap(t(rfe.set.mat),
        col=my_palette,
        border=TRUE,
        cluster_rows=FALSE,
        clustering_distance_columns = "euclidean",
        clustering_method_columns = "complete",
        show_row_names = FALSE,
        column_names_rot = 90,
        column_names_centered = FALSE,
        show_heatmap_legend = FALSE,
        heatmap_legend_param = list(title = "Predictive\nImportance"),
        rect_gp = gpar(col = "black", lwd = 1),
        column_dend_side = "bottom",column_names_side = "bottom")
```

@@

Heatmap(t(rfe.set.mat),
        col=my_palette,
        border=TRUE,
        cluster_rows=FALSE,
        clustering_distance_columns = "euclidean",
        clustering_method_columns = "complete",
        show_row_names = FALSE,
        column_names_rot = 90,
        column_names_centered = FALSE,
        show_heatmap_legend = FALSE,
        heatmap_legend_param = list(title = "Predictive\nImportance"),
        rect_gp = gpar(col = "black", lwd = 1),
        column_dend_side = "top",column_names_side = "top")
```
